---
title: "Data Visualization"
author: "Alex Rogers"
output: html_document
---



```{r}
library(dplyr)
library(ggplot2)
library(readr)

nc <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vTm2WZwNBoQdZhMgot7urbtu8eG7tzAq-60ZJsQ_nupykCAcW0OXebVpHksPWyR4x8xJTVQ8KAulAFS/pub?gid=202410847&single=true&output=csv")

```



### Exercise 1

R is considering the variable habit to be a character type variable.


What is going on with my Y axis labels when I run this code?:


ggplot(data = nc, aes(x = weeks, y = weight)) + 
  geom_point()
  
  
  
  
  
  I am uploading this code to save it. When I generate the scatterplot my y axis labels are overlapping and messy. I am going to try starting over. I also noticed an error when I loaded the spreadsheet, that I was missing a library called curl so it was using url instead. I'm going to try to install the curl package.


I instaleld the curl package and the labels on the y axis are showing as I expected. I'm not sure if installing the package or restarting R fixed the problem. Next time I'll save and just try relaunching R first.

I also noticed that before these changes the data frame had 743 entries, now it has 800 (still not the 1000 moderndive says there should be)


### Exercise 2

There is a positive relationship between length of pregnancy and birth weight of baby.

### Exercise 3

```{r}

ggplot(nc, aes(weeks, gained)) +
geom_point() +
labs(x = "Length of Pregnancy (weeks)", y = "Weight Gained by Mother (lbs)", title = "Relationship between pregnancy duration and mother's weight gained")



```

Okay so that worked but why is it only showing up to twelve weeks? The lowest value in the data frame is 20 and the highest is 45. I actually have no idea what the x axis is representing

jk I figured it out I had weight in the x axis argument for ggplot instead of weeks... trying again
```{r}

ggplot(nc, aes(weeks, gained)) +
geom_point() +
labs(x = "Length of Pregnancy (weeks)", y = "Weight Gained by Mother (lbs)", title = "Relationship between pregnancy duration and mother's weight gained")



```
holy shit I did it.

jk I didn't. now when I got to knit the markdown file I get the following error: "processing file: Rogers_HW2.Rmd
Quitting from lines 37-44 (Rogers_HW2.Rmd) 
Error in ggplot(nc, aes(weeks, gained)) : 
  could not find function "ggplot"
Calls: <Anonymous> ... handle -> withCallingHandlers -> withVisible -> eval -> eval

Execution halted"

Same problem after deleting the code chunk, now the problem is coming from the following code chunk. I know I have ggplot loaded because I can run the code from the console. wtf is going on? it also runs the code when I run it from the markdown document, just can't knit.


Alright I'm a goddamned genius. I didn't understand that you needed to open the library in the rmarkdown document, I figured if you had loaded it in the console it would apply to the markdown file (which doesn't really make sense in hindsight). I've loaded the necessary libraries and the data frame from the google sheet and it's actually working.