---
title: "Rogers_PS03"
output: html_document
author: Alex Rogers
---


```{r}

library(ggplot2)
library(dplyr)
data(txhousing)



```

### Question 1

The last city listed in the data frame is Wichita Falls.

### Question 2

The listings variable in this data set is the number of total active listings


### Question 3

```{r}

txhousing <- txhousing |> select(-inventory)

```


### Question 4

```{r}

dallas_sub <- txhousing |> filter(city == "Dallas", (year == 2012| year == 2013))

```


### Question 5

```{r}

dallas_sub <- dallas_sub |> 
  mutate(prct_sold = (sales/listings * 100) )

```


### Question 6

```{r}

dallas_summary <- dallas_sub |> 
  group_by(month) |> 
  summarize(mean (prct_sold))


```

### Question 7


```{r}

dallas_sub |> 
  arrange(desc(prct_sold))


```

Something isn't working here and I'm not sure why.

I had the code here as:

dallas_summary |> 
  arrange(desc(prct_sold))


But when I run it that way (with the data frame as dallas_summary instead of dallas_sub) I get an error that says the object prct_sold is not found. When I look at the data frame for dallas_summary I can see the prct_sold column is there (though it says "mean(prct_sold)"). I was thinking maybe that is the name of the column, but pointing to the object "mean(prct_sold)" doesn't work either. I'm stumped.


### Question 8

```{r}

txhousing |> 
  filter(year == 2012 | year == 2013, city == "Dallas") |> 
  mutate(prct_sold = sales/listings *100) |> 
  group_by(month) |> 
  summarize(mean_prct_sold = mean(prct_sold)) |> 
  arrange(desc(mean_prct_sold))


```
This code chunk calculated the percentages of home sold (of those listed) by month in 2012 and 2013. I think because of the "group_by(month)" function, it combined the months (e.g january 2012 and 2013 are combined and the average given).

This was achieved by:

filtering to show only 2012 OR 2013.

mutating to create a new variable (percent of homes listed vs sold)

calculating the mean of those percents (summarize)

ordering them starting with the highest value (arrange)


### Question 9


```{r}

least <- txhousing |> 
  filter(year == 2015 & month == 1) |> 
  arrange(listings)


```

San Marcos had the fewest listings in January 2015.


### Question 10


```{r}
txhousing |> 
  select (sales, month, year) |> 
  filter(year == 2012) |> 
  arrange(desc(sales))




```

The most houses were sold in Texas in 2012 in August.


### Question 11



```{r}

  PS03_sales <- txhousing |> 
  select(year, sales, city) |> 
  filter(year == 2001 | year == 2000, (city == "Dallas" | city == "Austin")) |> 
  select(sales)


  sum(PS03_sales)




  


```


That was hard.