---
title: "Rogers_HW3"
author: "Alex Rogers"

output: html_document
---

Hi Nico, sorry you have to read all this mess. This shit is so hard for me.


```{r}

library(tidyverse)

deck <- tibble(
  # tibble is a more flexible data.frame
  card = rep(
    c("ace",
      "deuce",
      "three",
      "four",
      "five",
      "six",
      "seven",
      "eight",
      "nine",
      "ten",
      "jack",
      "queen",
      "king"
    ),4),
  suit =
    rep(c(
      "diamonds", 
      "hearts", 
      "clubs", 
      "spades"),
        each = 13),
  color = rep(c("red", 
                "black"),
              each = 26)
)

glimpse(deck)


pr_black <- deck %>% 
  filter(color == "black") %>% 
  nrow()/nrow(deck)

pr_ace <- deck %>% 
  filter(card == "ace") %>% 
  nrow()/nrow(deck)

pr_black_and_ace <- deck %>% 
  filter(card == "ace" & color == "black") %>% 
  nrow()/nrow(deck)

pr_black + pr_ace - pr_black_and_ace

```

### Question 1


```{r}

pr_black * pr_black


```

This seems logical to me, since we only have two options in each event, it's like flipping a coin twice.


Part 2: Probability of getting one king or one ace: $king \cup ace$. Using naive probability this is number of aces or kings (8) / total number of cards (52)



```{r}

pr_ace_or_king <- 
deck |> 
filter(card == "ace" | card == "king")
nrow(pr_ace_or_king)/nrow(deck)


```

Part 3: Probability of getting two aces in two draws with replacement: 4/52 * 4/52

```{r}

pr_ace <- deck |> 
  filter(card == "ace") |> 
nrow()/nrow(deck)
  pr_ace * pr_ace
  
```

### Question 2


```{r}

sample_n(deck, size =5, replace = FALSE)
sample_n(deck, size =5, replace = FALSE)
sample_n(deck, size =5, replace = FALSE)
sample_n(deck, size =5, replace = FALSE)
sample_n(deck, size =5, replace = FALSE)


```

What is the total number of different hands you can draw in poker? This is asking us to do (I think) 52 choose 5 $\binom{52}{5}$

By googling I found that there is a function in the base R library that does this

(turns out I didn't need to google this, I just needed to finish reading the chapter)

```{r}

choose(52, 5)


```

### Question 3

The probability that each suit is represented in a hand (getting 1 card from each suit, with one suit showing up twice)


```{r}

pr_hearts <- deck |> 
  filter(suit == "hearts")
nrow(pr_hearts)/nrow(deck)

pr_spades <- deck |> 
  filter(suit == "spades")
nrow(pr_spades)/nrow(deck)

pr_diamonds <- deck |> 
  filter(suit == "diamonds")
nrow(pr_diamonds)/nrow(deck)

pr_clubs <- deck |> 
  filter(suit == "clubs")
nrow(pr_clubs)/nrow(deck)

```


I'm not sure what I was going for here but this was not a helpful direction, I'm saving the code and moving on to a different method.


I'm using the full house in poker example (1.4.20) from Blitztein and Hwang as a guide here.


4 Suits, 1 of each 3 times, 1 of the same 2 times (without replacement.
```{r}

# this is a syntactical nightmare. 
#(4*(choose(52, 1)* 3*(choose(51, 1) * 2*(choose(50, 1) * 1 *(49, 1))))


```



trying again 


```{r}

(4*choose(4, 1) * 3 * choose(4, 1) * 2 * choose(4, 1) * 1 * choose(4, 2)) / choose(52, 5)

```
That feels like a reasonable probability?


### Question 4

What is the probability of getting at least one ace in a five card hand?

So, the probability of getting one ace in one draw is 4/52.

How do I expand that to drawing 5 cards instead of one?

I think this is similar to the previous question, I understand that I need to use the binomial theorem (I think) but the syntax of trying to do this in R is really throwing me.



Okay, joke's on me, I hadn't read the R section of the chapter for this week, if I had done that this all would have been a lot easier.

Double joke's on me, I've read the whole thing and I'm still not getting it.


Probability of getting 1 ace in one 5-card hand:
```{r}

# I'm trying to approach the problem from a more simple perspective

draws <- (replicate(100, (sample)(52,5)))



# this draws 5 cards 100 times, obviously I would need more (e.g.) 10^4 in order to get a good probability estimate, but I'm trying to keep it simple for now.

#So this gives me the data frame "draws". I want to count how many times a 1,2,3,4 (1:4) appears across the data frame, thus counting how many times an ace was drawn. I can then divide that by the total number of cards drawn and I think that would give me the probability of drawing an ace.

#filter(draws, 5 == "1")

#What I'm trying here is to use the filter function to look at row 5 and show only times when a 5 was drawn, this isn't working. I think I need a  tibble with named rows and columns to do this?

#sample(deck, size = 4)

# I realized I'm basically trying to rebuild a tool I already have, which is the deck tibble from earlier in the hw. but now when I try to sample that I get the error "cannot take sample large than the population when 'replace = FALSE'

#but I'm trying to take a sample of 5 with a population of 52 so I don't get that.

#okay so sample(deck, 1) gives me a tibble with just the colors, sample(deck, 2) gives me a tibble with the colors and the card and so on until sample(deck, 4) gives the previous error. So either my syntax is off or I just can't use sample on this tibble (maybe because it's not intergers?) checking out ?sample

#I've been at this question for a couple hours now, getting discouraged, moving on.


```


Okay I'm gonna try again since I was able to mostly figure out the rest of the homework.

The probability of getting an ace is:

first card: 4/52
second card: 4/51
third card: 4/50
fourth card: 4/49
fifth card: 4/48

This isn't right though because it's not 4/51 as the second card if we draw an ace on the first card.

Gonna  try following the birthday problem example.

```{r}


1 - ((52 * 51 * 50 * 49 * 48) / 52^5)

```



So I am using the formula 

1 - 52 * 53... (52 - k + 1) /
52^k


I'm worried this is wrong though, 17 % feels low?

### Question 5


Clunky solution: 


```{r}

df <- tibble(
  id   = 1:6,
  name = c('Alice', 'Bob', 'Charlie', 'Diane', 'Fred', 'Jenny')
)

df_pairs <- df %>% 
  rename(id1 = id, name1 = name) %>% 
  crossing(df %>% 
             select(id2 = id, name2 = name)) %>%
  filter(id1 < id2) %>%
  unite(id, id1, id2) %>%
  unite(name, name1, name2)

df_pairs


```




This is a committee or "choose" problem so one way to do this is:

```{r}
choose(6,2)


```

I can verify this by listing out the possible pairs assuming order doesn't matter.

12 13 14 15 16 23 24 25 26 34 35 36 45 46 56

### Question 6

Removing the line  "filter(id1 < id2) %>%" almost does it, but it then allows a person to be the president and vice president, which I assume we don't want.

Trying something different...

```{r}

df <- tibble(
  id   = 1:6,
  name = c('Alice', 'Bob', 'Charlie', 'Diane', 'Fred', 'Jenny')
)

df_pairs <- df %>% 
  rename(id1 = id, name1 = name) %>% 
  crossing(df %>% 
             select(id2 = id, name2 = name)) %>%
  filter(id1 != id2) %>%
  unite(id, id1, id2) %>%
  unite(name, name1, name2)

df_pairs


```

I think I did it by using filter and != (not equal) to only show cases where the two names are not the same (thus ensuring that order does matter)


As for an analytic solution, we could do:


```{r}

(factorial(6)) / (factorial(6-2) * factorial(2))


```

Right so one of these is definitely wrong (possibly both)

I'm looking at the tibble and it makes logical sense to me so I think my factorial code is wrong somehow. I must not be correcting for overcounting properly.

```{r}

(factorial(6)) / (factorial(6-2))


```

Okay, I was using the formula where order didn't matter.


### Question 7

A fair die:

```{r}

die <- (1:6)

fair_die <- replicate(1000, sample(die, 1))

fair_die_data <- tibble(x = fair_die)

mean(fair_die)
```

A loaded die that lands on six 50% of the time

```{r}


 die <- (1:6)

six_die <- replicate(1000, sample(die, 1, prob = c(.1, .1, .1, .1, .1, .5)))

six_die_data <- tibble(x = six_die)

mean(six_die)

```

A loaded die that lands on 5 with p = 1/3 and 6 with p = 1/3


```{r}

 die <- (1:6)

thirds_die <- replicate(1000, sample(die, 1, prob = c(.1, .1, .1, .1, .3, .3)))

thirds_die_data <- tibble(x = thirds_die)

mean(thirds_die)

```


Fair die plot:

```{r}

ggplot(fair_die_data, aes(x = x)) +
  geom_histogram(color = "white", fill = "darkorchid") +
  labs(x = "Die roll (1 - 6)", y = "Number of rolls at given value", title = "A fair die")


```


Six Die Plot:

```{r}

ggplot(six_die_data, aes(x = x)) +
  geom_histogram(color = "white", fill = "darkorchid") +
  labs(x = "Die roll (1 - 6)", y = "Number of rolls at given value", title = "A six-weighted die")


```

Thirds Die Plot:

```{r}

ggplot(thirds_die_data, aes(x = x)) +
  geom_histogram(color = "white", fill = "darkorchid") +
  labs(x = "Die roll (1 - 6)", y = "Number of rolls at given value", title = "A thirds-weighted die")


```


```{r}

die <- (1:6)

test_die <- replicate(1000, sample(die, 1))

test_die_data <- tibble(Roll_Value = test_die)

mean(test_die)



```


